Solving Consensus with OpenFlow

### 2015-02-24 inband-STN.tex
blabla
added efficient alg.

%\usepackage[caption=true,font=footnotesize]{subfig}
%\usepackage{xspace} 	% Guesses whether a space is needed when invoked
\usepackage{cite}
%\usepackage{framed}
\usepackage{framed,color}
\definecolor{shadecolor}{rgb}{0.9,0.9,0.9}
%
%\usepackage{comment}

@@

\section{Fundamental Idea}\label{sec:background}

@@

\section{One-Touch Policy Update}\label{sec:realization}

SDN switch configuration space as shared memory

@@

Our first observation is that a match-action configuration which is accessed by multiple controllers can be considered as shared memory. Note however that standard memory map and index/offset to a word, while Flow Table entries are not indexed. To overcome this we can use the match part of an entry as the index and the action part as the word value.

@@

@@

\section{Discussion and Extensions}\label{sec:extension}

@@

\section{Improving the scheme with advanced OpenFlow features}\label{sec:todo}

TBD - much less resources. easily solving the infinite versions issue.

>>>>

%\usepackage[caption=true,font=footnotesize]{subfig}
%\usepackage{xspace} 	% Guesses whether a space is needed when invoked
\usepackage{cite}
%\usepackage{framed}
\usepackage{framed,color}
\definecolor{shadecolor}{rgb}{0.9,0.9,0.9}

%\usepackage{algorithm}
%\usepackage[noend]{algorithmic}

\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{algorithm}
\algrenewcommand\algorithmicreturn{\State \textbf{return}}
\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%

\algdef{SE}[TRANSACT]{StartTransaction}{EndTransaction}{\algorithmicaaa}[1]{\algorithmicwhile\ #1}%

\algblock[<block>]{<start>}{<end>}
\algblockdefx[Transaction]{startTransaction}{endTransaction} %
[0]{ \textbf{start transaction}} %
[1][res]{ $#1\gets$  \textbf{commit transaction}}

%
%\usepackage{comment}

@@

\section{The Underlying Theory}\label{sec:background}

@@

\section{Basic One-Touch Mechanism}\label{sec:realization}

@@

\subsection{SDN switch configuration space as shared memory}

Our first observation is that a match-action configuration which is accessed by multiple controllers can be considered as shared memory. Note however that standard memory map and index/offset to a word, while Flow Table entries are not necessarily indexed. However, we assume that each flow entry has some property that allows the operator to specifically reference and update it, for example OpenFlow entry's cookie. In cases where this property value can't be determined by the operator, we can use other variable entry properties to store the index, for example we can represent memory value $v$ in offset $i$ by an match-action entry whose match is $in\_port = i$ and action is "forward port $x$".
%To overcome this we can use the match part of an entry as the index and the action part as the word value.

@@

\subsection{ One-Touch}

@@

\section{The Practical Implementation}\label{sec:extension}

@@

\section{Improving the scheme with advanced OpenFlow features}\label{sec:todo}
Till now we considered a model that allows multiple updates to match-action entries. Here we extends the model with actions create-entry and delete-entry that may failed and abort the whole transaction depending on the existence on non-existence of specific entries prior to the action.
%TBD - much less resources. easily solving the infinite versions issue.

Next we show how such actions can be used to implement consensus with much less resources. We use entry id as a property used to reference specific entry.

\begin{algorithm}[t]
    \caption{Advanced Update Algorithm}
    \label{alg:template}
    \begin{algorithmic}[1]    
    \Require update requests $U$
    \Ensure installed policy is consistent with previous one
    \If {first time}
		%\Do 
		\Repeat 
			\State $my\_cur\_id\gets$ unused entry id 
    		\State $res \gets $ create entry with id $my\_cur\_id$
    	\Until{$res=False$}
    	%\doWhile{$res=False$}
    \EndIf
 		%\Do 
 		\Repeat 
 			\State $cur\_id\gets$ read current entry id 
 			\State $cur\_policy\gets$ read current policy
 			\State $my\_next\_id\gets$ unused entry id 
 			\State $new\_policy\gets$ apply update requests on $cur\_policy$
 			\startTransaction
	 			\State delete entry with id $1<<(\log n) + cur\_id$
	 			\State create entry with id $1<<(\log n) + my\_cur\_id$
	 			\State add $new\_policy$ rules conditioned on $metadata=my\_cur\_id$
	 			\State update policy selector to $my\_cur\_id$
 			\endTransaction
     		\State $res \gets $ commit transaction 
     	\Until{$res=False$}
     	%\doWhile{$res=False$}
%   \vspace{3mm}

    \end{algorithmic}
\end{algorithm}
